An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-22 VLDB2026/main.tex
Update main.tex

	As illustrated in Figure~\ref{fig:exp_3_1}, the evaluated algorithms exhibit varying degrees of sensitivity to attribute distribution shifts. \textcolor{cyan}{The proximity of the four curves (representing different attribute distributions) in the figure reflects the algorithm's sensitivity to distributional variations. When the curves converge closely, the algorithm demonstrates strong resilience against attribute distribution shifts. Conversely, greater divergence among the curves indicates higher distributional dependence. Accordingly, the "Strong" label signifies robust performance consistency across varying distributions, while "Weak" denotes pronounced performance fluctuations under distributional changes.} Specifically, ACORN, Milvus, Puck, CAPS, StitchedVamana, and UNG demonstrate strong robustness to such shifts. In contrast, Faiss, FilteredVamana, NHQ, VBASE, and PASE show notable sensitivity.

@@

	In contrast, VBASE exhibits the weakest robustness. As a post-filtering system, it performs significantly better under uniform distributions but degrades under long-tailed, normal, and power-law distributions. This degradation stems from the low selectivity of certain attributes in the last 3 distributions, which increases unnecessary distance computations, thus reducing overall efficiency.

>>>>

	As illustrated in Figure~\ref{fig:exp_3_1}, the evaluated algorithms exhibit varying degrees of sensitivity to attribute distribution shifts. \textcolor{cyan}{The proximity of the four curves (representing different attribute distributions) in the figure reflects the algorithm's sensitivity to distributional variations. When the curves converge closely, the algorithm demonstrates strong resilience against attribute distribution shifts. Conversely, greater divergence among the curves indicates higher distributional dependence. Accordingly, the "Strong" label signifies robust performance consistency across varying distributions, while "Weak" denotes pronounced performance fluctuations under distributional changes.} Specifically, ACORN, Milvus, Puck, CAPS, StitchedVamana, and UNG demonstrate strong robustness to such shifts. In contrast, Faiss, FilteredVamana, NHQ, and VBASE show notable sensitivity.

@@

	\textcolor{cyan}{In contrast, FilteredVamana achieves optimal performance under long-tail and uniform distributions, as these enable construction of balanced label subgraphs with minimal inter-label interference, thus improving search accuracy and efficiency. However, its performance declines under power-law and normal distributions: power-law distributions cause excessive concentration of popular labels and fragmentation of niche labels, disrupting search path connectivity, while normal distributions produce ambiguous graph structures due to label frequency similarities, leading to search divergence. The search performance of VBASE exhibits a direct dependence on attribute selectivity. As selectivity decreases, search speed declines. Notably, only uniform distribution maintains sufficient selectivity among the tested cases; the other three distributions consistently show low selectivity levels that significantly degrade VBASE's operational efficiency.}
